Tuning Low Frequency Pulsar Searching with an Artificial Pulsar Device

### 2020-12-03 ms.tex
Updates from Overleaf

 Then we need to apply the effects of dispersion to the pulse signal. According to e.g., \citet{2012hpa..book.....L}, the delay of frequency $\nu$ that is caused by the dispersion can be calculated as 
 \begin{gather}
     \Delta t(\nu)\simeq 4.15\times 10^6~{\rm ms}~\left(\frac{{\rm MHz}}{\nu}\right)^2\frac{\rm DM}{\rm pc~cm^{-3}}.
 \end{gather}
 So that the frequency dependent pulse profile after the dispersion effect is applied can be calculated as
 \begin{gather}
     f^{\rm d}(\nu, \theta)=f(\nu, \theta-\Delta t(\nu)/\tau),
 \end{gather}
where $\tau$ is the period of the pulsar. 
We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm10_profile}. The DM is assumed to be 10.0 and other parameters are same as what we set in Figure \ref{fig:dm0_profile}.

 \begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm10_profile.pdf}
    \caption{Frequency dependent pulse profile with a $\rm DM=10$ dispersion effect applied. The parameter of the pulsar
    is same as the one used in Figure \ref{fig:dm0_profile}}
    \label{fig:dm10_profile}
 \end{figure}

@@

@@

The PFB outputs the baseband I/Q sampling time series, which is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
The RF signal is fed into a power amplifier and broadcast through a proper antenna.

>>>>

 \subsubsection{Applying the dispersion effect}

 Then we need to apply the effects of dispersion to the pulse signal. According to e.g., \citet{2012hpa..book.....L}, the delay of frequency $\nu$ that is caused by the dispersion can be calculated as 
 \begin{gather}
     \Delta t(\nu)\simeq 4.15\times 10^6~{\rm ms}~\left(\frac{{\rm MHz}}{\nu}\right)^2\frac{\rm DM}{\rm pc~cm^{-3}}.
 \end{gather}
 So that the frequency dependent pulse profile after the dispersion effect is applied can be calculated as
 \begin{gather}
     f^{\rm d}(\nu, \theta)=f(\nu, \theta-\Delta t(\nu)/\tau),
 \end{gather}
where $\tau$ is the period of the pulsar. 
We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm1_profile}. The DM is assumed to be 10.0 and other parameters are same as what we set in Figure \ref{fig:dm0_profile}.

 \begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{dm1_profile.pdf}
    \caption{Frequency dependent pulse profile with a $\rm DM=1$ pc cm$^{-3}$ dispersion effect applied. The parameter of the pulsar
    is same as the one used in Figure \ref{fig:dm0_profile}}
    \label{fig:dm1_profile}
 \end{figure}

\subsubsection{Generating the narrow band I/Q sampling data}

@@

\subsubsection{Generating baseband I/Q sampling data stream}

@@

The PFB outputs the baseband I/Q sampling time series.
We plot a sample of the baseband I/Q sample data in Figure \ref{fig:iq_data}(a), the DM of which is $1$ pc cm$^{-3}$.
It is obvious that all apparent time domain feature has been smeared because of the dispersion, so that pure time domain analysis is hardly possible to detect the fake pulsar we simulated here.
As a comparison, we present the same plot of the I/Q data with DM=0 pc cm$^{-3}$ in Figure \ref{fig:iq_data}(b), in which pulse-like time domain structure can be recognized clearly.
The I/Q sampling data stream is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
The RF signal is fed into a power amplifier and broadcast through a proper antenna.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{dm1_iq.pdf}\\
    \includegraphics[width=0.95\columnwidth]{dm0_iq.pdf}
    \caption{The real part of the baseband I/Q data as a function of time. Two periods are shown here. The period is set to be 20 ms, in (a) the DM is set to be 10 pc cm$^{-3}$ and in (b), the DM is set to be 0 pc cm$^{-3}$ for the purpose of comparison.}
    \label{fig:iq_data}
\end{figure}
